---
output: github_document
always_allow_html: true
editor_options: 
  markdown: 
    wrap: 72
  chunk_output_type: console
#bibliography: references.bib
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)

library(tidyverse)
```

# wsabrazil

<!-- badges: start -->
[![License: CC BY 4.0](https://img.shields.io/badge/License-CC_BY_4.0-lightgrey.svg)](https://creativecommons.org/licenses/by/4.0/)
<!-- badges: end -->

This package contains information related to waste management practices and household infrastructure across various regions in Brazil. It includes variables such as sector codes, metropolitan region names, municipality codes, and names, as well as data on the location type, living conditions, average income, and household amenities. The data provides insights into waste disposal habits, water supply sources, bathroom facilities, and sanitation infrastructure in Brazilian households, contributing to understanding environmental sustainability and infrastructure development efforts.

## Installation

You can install the development version of wsabrazil from [GitHub](https://github.com/) with:

```r
# install.packages("devtools")
devtools::install_github("openwashdata/wsabrazil")
```

Alternatively, you can download the dataset as a CSV or XLSX
file from the table below.

```{r, echo=FALSE, message=FALSE, warning=FALSE}

extdata_path <- "https://github.com/openwashdata/wsabrazil/raw/main/inst/extdata/"

read_csv("data-raw/dictionary.csv") |> 
  distinct(file_name) |> 
  dplyr::mutate(file_name = str_remove(file_name, ".rda")) |> 
  dplyr::rename(dataset = file_name) |> 
  mutate(
    CSV = paste0("[Download CSV](", extdata_path, dataset, ".csv)"),
    XLSX = paste0("[Download XLSX](", extdata_path, dataset, ".xlsx)")
  ) |> 
  knitr::kable()

```

## Data

The dataset includes observations of waste management practices and household infrastructure (access to water and sanitation services) across various regions in Brazil.

The package provides access to one single dataset.

```{r, echo = TRUE}
library(wsabrazil)
```

The `wsabrazil` dataset has `r ncol(wsabrazil)`
variables and `r nrow(wsabrazil)` observations. For an overview
of the variable names, see the following table.

```{r, eval=FALSE}
wsabrazil
```

```{r, echo=FALSE, message=FALSE, warning=FALSE}
readr::read_csv("data-raw/dictionary.csv") |> 
  dplyr::filter(file_name == "wsabrazil.rda") |> 
  dplyr::select(variable_name:description) |> 
  knitr::kable() |> 
  kableExtra::kable_styling() |> 
  kableExtra::scroll_box(height = "400px")
```

## Example

## License

## Citation

To cite this package, please use:

```{r}
citation("wsabrazil")
```
